\documentclass[10pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{classic}        % Style options: casual, classic, banking, oldstyle, fancy
\moderncvcolor{blue}           % Color options: blue, burgundy, green, grey, orange, purple, red

% Character encoding
\usepackage[utf8]{inputenc}

% Adjust page margins
\usepackage[scale=0.75]{geometry}

% Personal Information
\name{Patrick}{Tierney}
\address{106th Ave NE}{Kirkland WA, 98033}
\phone[mobile]{+1~(319)~330~5881}
\email{ptierney13@gmail.com}

\begin{document}

%----- Cover Letter -----
\recipient{Hiring Manager}{Riot Games}
\date{\today}
\opening{Dear Hiring Manager,}
\closing{Sincerely,}

\makelettertitle

I am writing to express my sincere interest in the Tools Engineering role at Riot Games. While my professional background is rooted outside the games industry, my career has been defined by a love for building and improving developer tooling to bring joy to my coworkers.  I have a deep passion for games and game design in my personal life, and the idea of working within and improving Riot's player-first development ecosystem truly excites me.  This role offers an opportunity to merge my personal and professional passions, so I hope we can discuss further how I can bring my drive and excitement for this project to Riot.

Professionally, I have spent years at Microsoft designing, building, and maintaining internal tools and developer workflows.  I have enabled my coworkers to safely and confidently move faster, and to focus on the work that matters most. I discovered a passion for truly delighting my coworkers by delivering tools or architectural solutions which made their jobs simpler.  I have spent the last five years of my career working with engineers, product managers, and leadership to identify pain points and common workflows, then designing and implementing tools to address these problems from the ground up.  Supporting others by improving their daily experience with thoughtful tooling has been the most fulfilling aspect of my career.  

Outside of work, games are a central passion for me, both as a social and a creative outlet. My strongest friendships from college were cemented playing intramural League of Legends, I played Magic: the Gathering at a professional level for years before COVID, and I spend most weekends playing board games, card games, or video games. I am an active participant in the Seattle Magic: the Gathering Cube design community, I run a Dungeons \& Dragons campaign heavily homebrewed to make it more interesting for D\&D veterans, and I have been known to stay up until the early morning debating TFT set design or, more recently, Riftbound card design.  I am deeply interested in player-focused design and creating engaging gameplay experiences, which is exactly the mindset Riot prides itself in. The opportunity to work closely with likeminded people and to express my personal passions professionally would be the perfect environment for me to succeed.

While I have not worked professionally in the games industry and have not used Unreal Engine since high school, I see this role as a uniquely strong fit. I was the point person for the Whiteboard team for onboarding us onto new Microsoft-wide offerings, so I am thoroughly practiced in ramping up on new tools and systems quickly.  I know from experience that when I am excited by the mission, I invest myself fully—and I would approach this role with the same energy and intensity that I bring to my personal passion projects. I am highly motivated to establish and deepen an expertise with Unreal Engine and modern game development workflows, and to stay current with new and emerging tools across the industry.

Thank you for taking the time to review my application. I would greatly appreciate the opportunity to discuss this role further, as I am confident that I would throw myself into this position with enthusiasm and dedication, quickly growing into an expert and contributing meaningfully to Riot’s tools ecosystem.

\makeletterclosing

\end{document}