\documentclass[12pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{classic}        % Style options: casual, classic, banking, oldstyle, fancy
\moderncvcolor{blue}           % Color options: blue, burgundy, green, grey, orange, purple, red

% Character encoding
\usepackage[utf8]{inputenc}

% Adjust page margins
\usepackage[scale=0.75]{geometry}

% Personal Information
\name{Patrick}{Tierney}
\address{106th Ave NE}{Kirkland WA, 98033}
\phone[mobile]{+1~(319)~330~5881}
\email{ptierney13@gmail.com}

\begin{document}

%----- Cover Letter -----
\recipient{Hiring Manager}{Riot Games}
\date{\today}
\opening{Dear Hiring Manager}
\closing{Sincerely,}

\makelettertitle

I am writing to express my sincere interest in the Services role at Riot Games. While my professional background is rooted outside the games industry, the majority of my career has been spent developing and maintaining the backend for Microsoft Whiteboard, a real-time collaboration tool used by millions.  I have a deep passion for games and game design in my personal life, and the idea of working within and improving Riot's player-first development ecosystem truly excites me.  This role offers an opportunity to merge my personal and professional passions, so I hope we can discuss further how I can bring my drive and excitement for this project to Riot.

Professionally, I have worked solely on the backend for internet scale systems, between Microsoft's Whiteboard, Edge, and more recently Copilot Hub.  I began my tenure at Microsoft translating Whiteboard into TypeScript, helping to rewrite the entirety of the backend system and services.  In this period, I also worked with a team of four other engineers to design and develop a new service for managing and querying a user's Whiteboards programmatically via public APIs.  I helped maintain the application-side communication protocols with two backend services concurrently for the C\# and TypeScript codebases respectively.  Later on in my time at Microsoft, I wanted to ensure we were building the best product possible for our customers, so I owned and improved our on-call, bug handling, and CI/CD pipelines for code deployment and testing.  This work led me to work closely with the team maintaining our backend service, improving observability of issues and developing best practices and playbooks for addressing outages.  So while I do not have experience working on game systems directly, I have developed expertise in building and maintaining a large-scale real-time collaboration tool.

Outside of work, games are a central passion for me, both as a social and a creative outlet. My strongest friendships from college were cemented playing intramural League of Legends, I played Magic: The Gathering at a professional level for years before COVID, and I spend most weekends playing board games, card games, or video games. I am an active participant in the Seattle Magic: The Gathering Cube design community, I run a Dungeons \& Dragons campaign heavily homebrewed to make it more interesting for D\&D veterans, and I have been known to stay up until the early morning debating TFT set design or, more recently, Riftbound card design.  I am deeply interested in player-focused design and creating engaging gameplay experiences, which is exactly the mindset Riot prides itself in. This opportunity to work closely with likeminded people and to express my personal passions professionally would offer the perfect environment for me to succeed.

I am extremely enthusiastic about this role.  Riot's games have had a huge impact on my life, and the idea of working with other developers who want to focus on making a truly wonderful player-first game excites me.   I know from experience that when I am excited by the mission, I invest myself fully—and I would approach this role with the same energy and intensity that I bring to my personal passion projects.  The chance to take what I've learned at Microsoft and make a real difference bringing joy to players' lives would mean the world to me.

Thank you for taking the time to review my application. I would greatly appreciate the opportunity to discuss this role further, as I am confident that I would throw myself into this position with enthusiasm and dedication, quickly growing into an expert in your system and contributing meaningfully to the services supporting this new unpublished project.

\makeletterclosing

\end{document}